Technique for \earlywarning\ filtering for compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-28 results.tex
addressed leos comments
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1172 ccdd05d5-56c1-461a-bf98-85f6876523b4

Even without further refinements, our implementation of the \lloid\ algorithm
achieves latencies that would make other aspects of the analysis the limiting
steps assuming that the human vetting process is removed.

>>>>

Even without further refinements, our implementation of the \lloid\ algorithm
achieves latencies that would make other aspects of the analysis the limiting
steps assuming that the human vetting process is automated.
